
```{r}
if (!require("dplyr")) {install.packages("dplyr")}
if (!require("readr")) {install.packages("readr")}
if (!require("ggplot2")) {install.packages("ggplot2")}
if (!require("tidyr")) {install.packages("tidyr")}
if (!require("reshape2")) {install.packages("reshape2")}
if (!require("fingertipsR")) {install.packages("fingertipsR")}
if (!require("sf")) {install.packages("sf")}
if (!require("factoextra")) {install.packages("factoextra")} # for PCA

```

```{r}
library(fingertipsR)
library(tidyverse)
library(fingertipscharts)
library(corrplot)
library(psych)
library(reshape2)
library(factoextra) # for PCA
```

```{r}
#profiles <- profiles()
#areas <- area_types()
```

```{r}
indicators <- indicators(ProfileID = 19) #there are 168 indicators in profileID 19 (PHOF)
```

```{r}
data <- fingertips_data(ProfileID = 19, AreaTypeID = 101)
```

```{r}
# Latest data for each District & UA, Indicator & General population

latest_data <- data %>% 
  group_by(IndicatorID, IndicatorName, Sex, Age, AreaName) %>%                     
  filter(TimeperiodSortable == max(TimeperiodSortable), AreaType == "District & UA", Sex == "Persons") #%>%
  #view()
#view(latest_data)

```

```{r}
# which indicators remain at this point?
latest_data_ind <- latest_data %>%
  group_by(IndicatorID) %>%
  distinct(IndicatorID) #%>%
  #view()
```
There are 84 indicators corresponding to the District & Local Authority area level, of which remain 72 indicators when filtering for the general population (i.e. Sex = Persons). This eliminates indicators which are designed for tracking the differences between the sexes, for example, "Life expectancy at birth" (Indicator ID 90366).
```{r}
# Identifying which indicators have the largest proportion of missing data 
# Credits to John Lomas
latest_data_missingprop <- latest_data %>% 
  group_by(TimeperiodSortable, IndicatorID, IndicatorName) %>% 
  summarise(n_missing = sum(is.na(Value)), 
            prop_missing = sum(is.na(Value))/n(), 
            n = n()) %>% 
  arrange(desc(prop_missing)) %>% 
  filter(prop_missing >= 0.15) #%>%
  #view()
  
```
The indicator with the largest proportion of missing values will be the less reliable at the time of calculating the index. The indicators "Deaths from drug misuse", "Treatment completion for TB", "HIV late diagnosis" have over 15% of missing data, but since their nature is of great importance to a healthcare landscape, these will be included in the analysis. Indicators "Statutory homelessness - Eligible homeless people not in priority need" and "Estimated diabetes diagnosis rate", the latter for the 2017 period only, since there is also one for the 2018 period, will be excluded.
```{r}
latest_data2 <- latest_data[ ! (( latest_data$TimeperiodSortable == 20170000 & latest_data$IndicatorID == 93347 ) 
                              | ( latest_data$TimeperiodSortable == 20170000 & latest_data$IndicatorID == 92314)) , ]
#view(latest_data2)
```

```{r}
# Imputation of missing data with the median value
# Credits to John Lomas and Anil.
data_w_median <- latest_data2 %>% 
  group_by(IndicatorID, IndicatorName) %>%
  select(TimeperiodSortable, IndicatorID, IndicatorName, AreaCode, AreaName, Value) %>%  
  mutate(Median = median(Value, na.rm = TRUE), Value_imputed = ifelse(is.na(Value), Median, Value)) %>%
  select(-c(AreaCode, Median, Value)) #%>%
  #view()

#view(data_w_median)
```

```{r}
# Transform the data from long to wide format
# Credits to Nanjo Atsunori
 data_wide <- xtabs(Value_imputed ~ AreaName + IndicatorID, data_w_median) %>%
   as.data.frame.matrix()
 #view(data_wide)
 
```

```{r}
# test of normality of Indicator values with Shapiro-Wilk test. If data for an indicator is not normal (p-value < 0.05)
# it normalises the data with the log 10 function. The function produces NA values for negative numbers or zeros, which later are replaced by median values.

not_normal_ind <- c()
i <- 1

for (col_name in colnames(data_wide)) {
  
  if (shapiro.test(as.numeric(data_wide[[col_name]]))$p.value < 0.05) { #if data is not normal it 
                                                                        #it normalises it with log10
    not_normal_ind[i] <- col_name                                       #function
    log10(data_wide[[col_name]])
    i <- i + 1
    
  }
}
```

```{r}
replace_w_median =function(x){
   
   x[is.na(x)] = median(x, na.rm=TRUE) # converts the value with NA to median value from the indicator
   x                                   # taken from Stack Overflow
   }
```

```{r}
normal_data = data.frame(apply(data_wide, 2, replace_w_median))
#view(normal_data)
```

```{r}
# Reverse polarity of indicators where a higher number means a better index.

normal_data$X93077 <- normal_data$X93077 * -1
normal_data$X93078 <- normal_data$X93078 * -1
normal_data$X93079 <- normal_data$X93079 * -1
normal_data$X93014 <- normal_data$X93014 * -1
normal_data$X91720 <- normal_data$X91720 * -1
normal_data$X91367 <- normal_data$X91367 * -1
normal_data$X92441 <- normal_data$X92441 * -1
normal_data$X91195 <- normal_data$X91195 * -1
normal_data$X92313 <- normal_data$X92313 * -1
normal_data$X90834 <- normal_data$X90834 * -1

```

```{r}
scaled_data <- data.frame(scale(normal_data))  # scales the data to z-scores of each indicator per area.
#view(scaled_data)
```

```{r}
# Calculation of Mean Z-score per Area
data_zmean <- scaled_data

data_zmean$MeanZ <- rowMeans(data_zmean)
#View(data_zmean)
```

```{r}
# Isolation of Mean Z-score for each area. This allows the ranking of each area's healthcare landscape considering every indicator
#at this point

area_meanz <- data_zmean %>%
  select(MeanZ) 

#view(area_meanz)
```

```{r}
# Correlation between indicators
# Credits to Nanjo Atsunori

data_cor_assignment <- cor(scaled_data)
corrplot(data_cor_assignment, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```

```{r}
# Principal Component Analysis

prin_comp <- prcomp(data_cor_assignment, scale. = FALSE, center = FALSE) # data has already been scaled and centered with the scale() function
names(prin_comp)
```

```{r}
prin_comp$rotation
```

```{r}
dim(prin_comp$x)
```

```{r}
#compute standard deviation of each principal component
std_dev <- prin_comp$sdev

#compute variance
pr_var <- std_dev^2

#check variance of first 10 components
 pr_var[1:10]
```

```{r}
# Eigenvalues
eig.val <- get_eigenvalue(prin_comp)
eig.val

```
With the first two Principal Components it's possible to explain 89% of the variance. The first dimension alone explains 80%, so we will focus on this one.

```{r}
fviz_eig(prin_comp, addlabels = TRUE, linecolor = "red")
```

```{r}
fviz_pca_ind(prin_comp,
             col.ind = "cos2", # Color by the quality of representation
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )
```

```{r}
fviz_pca_var(prin_comp,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )
```

Indicators for influencing the first Principal Component ranked according to influence.
```{r}
pc_1 <- prin_comp$x[,1]
pc_1 <- sort(abs(pc_1), decreasing = TRUE)
pc_1
```
```{r}
fviz_cos2(prin_comp, choice = "var", axes = 1)
```
```{r}
fviz_contrib(prin_comp, choice = "var", axes = 1, top = 31)
```

```{r}
# For easier lookup of the most relevant indicators

datawmedian_eachid <- data_w_median %>%
  select(IndicatorID, IndicatorName) %>%
  group_by(IndicatorID) %>%
  distinct() #%>%
  #view()
```

```{r}
# Recalculation of Composite Health Index with only the top 5 indicators from each health outcome measures, modifiable risk factors and 
# social determinants of health obtained with PCA

top5_sg <- c(40401, 40701, 40402, 40502, 40702, # Health outcome measures
             91872, 90630, 11201, 90356, 11202, # Social determinants of health
             20602, 93077, 93015, 20601, 92443) # Modifiable risk factors

top5_df<- data %>% 
  group_by(IndicatorID, IndicatorName, Sex, Age, AreaName) %>%                     
  filter(TimeperiodSortable == max(TimeperiodSortable), AreaType == "District & UA", Sex == "Persons", IndicatorID %in% top5_sg) #%>%
  #view()
#view(top5_df)

# Imputation of missing data with the median value
# Credits to John Lomas and Anil.

top5_w_median <- top5_df %>% 
  group_by(IndicatorID, IndicatorName) %>%
  select(TimeperiodSortable, IndicatorID, IndicatorName, AreaCode, AreaName, Value) %>%  
  mutate(Median = median(Value, na.rm = TRUE), Value_imputed = ifelse(is.na(Value), Median, Value)) %>%
  select(-c(AreaCode, Median, Value)) #%>%
  #view()

# Transform the data from long to wide format
# Credits to Nanjo Atsunori
 top5wide <- xtabs(Value_imputed ~ AreaName + IndicatorID, top5_w_median) %>%
   as.data.frame.matrix()
 #view(top15wide)

# test of normality of Indicator values with Shapiro-Wilk test. If data for an indicator is not normal (p-value < 0.05)
# it normalises the data with the log 10 function. The function produces NA values for negative numbers or zeros, which are replaced by median values.

top5_notnormalind <- c()
i <- 1

for (col_name in colnames(top5wide)) {
  
  if (shapiro.test(as.numeric(top5wide[[col_name]]))$p.value < 0.05) { #if data is not normal it 
                                                                        #it normalises it with log10
    top5_notnormalind[i] <- col_name                                   #function
    log10(top5wide[[col_name]])
    i <- i + 1
    
  }
}

#view(top15_notnormalind)

top5_normaldata = data.frame(apply(top5wide, 2, replace_w_median))
#view(top15_normaldata)

# Polarity reversal
top5_normaldata$X93077 <- top5_normaldata$X93077 * -1

top5scaled_sg <- data.frame(scale(top5_normaldata))  # scales the data to z-scores of each indicator per area.
#view(top15scaled)

# Calculation of Mean Z-score per Area
top5zmean <- top5scaled_sg

top5zmean$MeanZ <- rowMeans(top5zmean)
#view(top15zmean)

# Isolation of Mean Z-score for each area. This allows the ranking of each area's healthcare landscape.

top5areameanz <- top5zmean %>%
  select(MeanZ) %>%
  rownames_to_column('Area') %>%
  mutate(Score = MeanZ * -1 + 10) %>%
  select(Area, Score) %>%
  arrange(desc(Score)) #%>%
  #view()
#view(top15areameanz)
```

```{r}
england_map <- st_read(dsn = "https://opendata.arcgis.com/datasets/25dc36af098744c6848f8228a09d87b3_0.geojson")
 
area_scores <- select(top5areameanz, Area, Score)

england_scores <- england_map %>% 
   left_join(y = area_scores, by = c("lad18nm" = "Area")) %>%
  select(Score, geometry) %>%
  filter(is.na(Score) == FALSE)

 plot(england_scores, main = "Aggregated Composite Health Index in England")
```

```{r}
Mean <- mean(top5areameanz$Score)
sdv <- sd(top5areameanz$Score)
Median <- median(top5areameanz$Score)

Mean
sdv
Median
```


```{r}
# Correlation between indicators
# Credits to Nanjo Atsunori

top5_cor <- cor(top5scaled_sg)
corrplot(top5_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```
```{r}
# Recalculation of REGIONAL Composite Health Index with only the top 5 indicators from health outcome measures, modifiable risk factors and 
# social determinants of health obtained with PCA

top5_sg <- c(40401, 40701, 40402, 40502, 40702, # Health outcome measures
             91872, 90630, 11201, 90356, 11202, # Social determinants of health
             20602, 93077, 93015, 20601, 92443) # Modifiable risk factors

top5_df<- data %>% 
  group_by(IndicatorID, IndicatorName, Sex, Age, AreaName) %>%                     
  filter(TimeperiodSortable == max(TimeperiodSortable), AreaType == "Region", Sex == "Persons", IndicatorID %in% top5_sg) #%>%
  #view()
#view(top5_df)

# Imputation of missing data with the median value
# Credits to John Lomas and Anil.

region_median <- top5_df %>% 
  group_by(IndicatorID, IndicatorName) %>%
  select(TimeperiodSortable, IndicatorID, IndicatorName, AreaCode, AreaName, Value) %>%  
  mutate(Median = median(Value, na.rm = TRUE), Value_imputed = ifelse(is.na(Value), Median, Value)) %>%
  select(-c(AreaCode, Median, Value)) #%>%
  #view()

# Transform the data from long to wide format
# Credits to Nanjo Atsunori
 region_wide <- xtabs(Value_imputed ~ AreaName + IndicatorID, region_median) %>%
   as.data.frame.matrix()
 #view(top15wide)

# test of normality of Indicator values with Shapiro-Wilk test. If data for an indicator is not normal (p-value < 0.05)
# it normalises the data with the log 10 function. The function produces NA values for negative numbers or zeros, which are replaced by median values.

top5_notnormalind <- c()
i <- 1

for (col_name in colnames(region_wide)) {
  
  if (shapiro.test(as.numeric(region_wide[[col_name]]))$p.value < 0.05) { #if data is not normal it 
                                                                        #it normalises it with log10
    top5_notnormalind[i] <- col_name                                   #function
    log10(region_wide[[col_name]])
    i <- i + 1
    
  }
}

#view(top15_notnormalind)

region_normaldata = data.frame(apply(region_wide, 2, replace_w_median))
#view(top15_normaldata)

# Polarity reversal
region_normaldata$X93077 <- region_normaldata$X93077 * -1

regionscaled_sg <- data.frame(scale(region_normaldata))  # scales the data to z-scores of each indicator per area.
#view(top15scaled)

# Calculation of Mean Z-score per Area
region_mean <- regionscaled_sg

region_mean$MeanZ <- rowMeans(region_mean)
#view(top15zmean)

# Isolation of Mean Z-score for each area. This allows the ranking of each area's healthcare landscape.

region_mean <- region_mean %>%
  rownames_to_column('Area') %>%
  mutate(Score = MeanZ * -1 + 10) %>%
  select(Area, Score) %>%
  arrange(desc(Score)) #%>%
  #view()

```

```{r}
# Recalculation of Health Index with only the top 5 indicators from health outcome measures obtained with PCA

topHOM <- c(40401, 40701, 40402, 40502, 40702) # Health outcome measures

topHOM_df<- data %>% 
  group_by(IndicatorID, IndicatorName, Sex, Age, AreaName) %>%                     
  filter(TimeperiodSortable == max(TimeperiodSortable), AreaType == "District & UA", Sex == "Persons", IndicatorID %in% topHOM) #%>%
  #view()
#view(top15_df)

# Imputation of missing data with the median value
# Credits to John Lomas and Anil.

topHOM_w_median <- topHOM_df %>% 
  group_by(IndicatorID, IndicatorName) %>%
  select(TimeperiodSortable, IndicatorID, IndicatorName, AreaCode, AreaName, Value) %>%  
  mutate(Median = median(Value, na.rm = TRUE), Value_imputed = ifelse(is.na(Value), Median, Value)) %>%
  select(-c(AreaCode, Median, Value)) #%>%
  #view()

# Transform the data from long to wide format
# Credits to Nanjo Atsunori
 topHOMwide <- xtabs(Value_imputed ~ AreaName + IndicatorID, topHOM_w_median) %>%
   as.data.frame.matrix()
 #view(top15wide)

# test of normality of Indicator values with Shapiro-Wilk test. If data for an indicator is not normal (p-value < 0.05)
# it normalises the data with the log 10 function. The function produces NA values for negative numbers or zeros, which are replaced by median values.

topHOM_notnormalind <- c()
i <- 1

for (col_name in colnames(topHOMwide)) {
  
  if (shapiro.test(as.numeric(topHOMwide[[col_name]]))$p.value < 0.05) { #if data is not normal it 
                                                                        #it normalises it with log10
    topHOM_notnormalind[i] <- col_name                                   #function
    log10(topHOMwide[[col_name]])
    i <- i + 1
    
  }
}

#view(top15_notnormalind)

topHOM_normaldata = data.frame(apply(topHOMwide, 2, replace_w_median))
#view(top15_normaldata)

topHOMscaled <- data.frame(scale(topHOM_normaldata))  # scales the data to z-scores of each indicator per area.
#view(top15scaled)

# Calculation of Mean Z-score per Area
topHOMzmean <- topHOMscaled

topHOMzmean$MeanZ <- rowMeans(topHOMzmean)
#view(top15zmean)

# Isolation of Mean Z-score for each area. This allows the ranking of each area's healthcare landscape.

topHOMareameanz <- topHOMzmean %>%
  select(MeanZ) %>%
  rownames_to_column('Area') %>%
  mutate(Score = MeanZ * -1 + 10) %>%
  select(Area, Score) %>%
  arrange(desc(Score)) #%>%
  #view()
#view(top15areameanz)

```

```{r}
#england_map <- st_read(dsn = #"https://opendata.arcgis.com/datasets/25dc36af098744c6848f8228a09d87b3_0.geojson")
# 
hom_scores <- select(topHOMareameanz, Area, Score)

hom_england <- england_map %>% 
   left_join(y = hom_scores, by = c("lad18nm" = "Area")) %>%
  select(Score, geometry) %>%
  filter(is.na(Score) == FALSE)

 plot(hom_england, main = "Health Outcome Measures in England")
```

```{r}
Mean <- mean(topHOMareameanz$Score)
sdv <- sd(topHOMareameanz$Score)
Median <- median(topHOMareameanz$Score)

Mean
sdv
Median
```

```{r}
# Correlation between indicators
# Credits to Nanjo Atsunori

topHOM_cor <- cor(topHOMscaled)
corrplot(topHOM_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```

```{r}

# Recalculation of Health Index with only the top 5 indicators from the Social determinants of health subgroup

top3SDH <- c(91872, 90630, 11201, 90356, 11202) # Social determinants of health

topSDH_df<- data %>% 
  group_by(IndicatorID, IndicatorName, Sex, Age, AreaName) %>%                     
  filter(TimeperiodSortable == max(TimeperiodSortable), AreaType == "District & UA", Sex == "Persons", IndicatorID %in% top3SDH) #%>%
  #view()
#view(top15_df)

# Imputation of missing data with the median value
# Credits to John Lomas and Anil.

topSDH_w_median <- topSDH_df %>% 
  group_by(IndicatorID, IndicatorName) %>%
  select(TimeperiodSortable, IndicatorID, IndicatorName, AreaCode, AreaName, Value) %>%  
  mutate(Median = median(Value, na.rm = TRUE), Value_imputed = ifelse(is.na(Value), Median, Value)) %>%
  select(-c(AreaCode, Median, Value)) #%>%
  #view()

# Transform the data from long to wide format
# Credits to Nanjo Atsunori
 topSDHwide <- xtabs(Value_imputed ~ AreaName + IndicatorID, topSDH_w_median) %>%
   as.data.frame.matrix()
 #view(top15wide)

# test of normality of Indicator values with Shapiro-Wilk test. If data for an indicator is not normal (p-value < 0.05)
# it normalises the data with the log 10 function. The function produces NA values for negative numbers or zeros, which are replaced by median values.

topSDH_notnormalind <- c()
i <- 1

for (col_name in colnames(topSDHwide)) {
  
  if (shapiro.test(as.numeric(topSDHwide[[col_name]]))$p.value < 0.05) { #if data is not normal it 
                                                                        #it normalises it with log10
    topSDH_notnormalind[i] <- col_name                                   #function
    log10(topSDHwide[[col_name]])
    i <- i + 1
    
  }
}

#view(top15_notnormalind)

topSDH_normaldata = data.frame(apply(topSDHwide, 2, replace_w_median))
#view(top15_normaldata)

topSDHscaled <- data.frame(scale(topSDH_normaldata))  # scales the data to z-scores of each indicator per area.
#view(top15scaled)

# Calculation of Mean Z-score per Area
topSDHzmean <- topSDHscaled

topSDHzmean$MeanZ <- rowMeans(topSDHzmean)
#view(top15zmean)

# Isolation of Mean Z-score for each area. This allows the ranking of each area's healthcare landscape.

topSDHareameanz <- topSDHzmean %>%
  select(MeanZ) %>%
  rownames_to_column('Area') %>%
  mutate(Score = MeanZ * -1 + 10) %>%
  select(Area, Score) %>%
  arrange(desc(Score)) #%>%
  #view()
#view(top15areameanz)

```

```{r}
#england_map <- st_read(dsn = #"https://opendata.arcgis.com/datasets/25dc36af098744c6848f8228a09d87b3_0.geojson")
# 
sdh_scores <- select(topSDHareameanz, Area, Score)

sdh_england <- england_map %>% 
   left_join(y = sdh_scores, by = c("lad18nm" = "Area")) %>%
  select(Score, geometry) %>%
  filter(is.na(Score) == FALSE)

 plot(sdh_england, main = "Social Determinants of Health in England")
```

```{r}
Mean <- mean(topSDHareameanz$Score)
sdv <- sd(topSDHareameanz$Score)
Median <- median(topSDHareameanz$Score)

Mean
sdv
Median
```

```{r}
# Correlation between indicators
# Credits to Nanjo Atsunori

topSDH_cor <- cor(topSDHscaled)
corrplot(topSDH_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```

```{r}

# Recalculation of Health Index with only the top 5 indicators from Modifiable risk factors subgroup obtained with PCA

topMRF <- c(20602, 93077, 93015, 20601, 92443) # Modifiable risk factors

topMRF_df<- data %>% 
  group_by(IndicatorID, IndicatorName, Sex, Age, AreaName) %>%                     
  filter(TimeperiodSortable == max(TimeperiodSortable), AreaType == "District & UA", Sex == "Persons", IndicatorID %in% topMRF) #%>%
  #view()
#view(top15_df)

# Imputation of missing data with the median value
# Credits to John Lomas and Anil.

topMRF_w_median <- topMRF_df %>% 
  group_by(IndicatorID, IndicatorName) %>%
  select(TimeperiodSortable, IndicatorID, IndicatorName, AreaCode, AreaName, Value) %>%  
  mutate(Median = median(Value, na.rm = TRUE), Value_imputed = ifelse(is.na(Value), Median, Value)) %>%
  select(-c(AreaCode, Median, Value)) #%>%
  #view()

# Transform the data from long to wide format
# Credits to Nanjo Atsunori
 topMRFwide <- xtabs(Value_imputed ~ AreaName + IndicatorID, topMRF_w_median) %>%
   as.data.frame.matrix()
 #view(top15wide)

# test of normality of Indicator values with Shapiro-Wilk test. If data for an indicator is not normal (p-value < 0.05)
# it normalises the data with the log 10 function. The function produces NA values for negative numbers or zeros, which are replaced by median values.

topMRF_notnormalind <- c()
i <- 1

for (col_name in colnames(topMRFwide)) {
  
  if (shapiro.test(as.numeric(topMRFwide[[col_name]]))$p.value < 0.05) { #if data is not normal it 
                                                                        #it normalises it with log10
    topMRF_notnormalind[i] <- col_name                                   #function
    log10(topMRFwide[[col_name]])
    i <- i + 1
    
  }
}

#view(top15_notnormalind)

topMRF_normaldata = data.frame(apply(topMRFwide, 2, replace_w_median))
#view(top15_normaldata)

topMRF_normaldata$X93077 <- topMRF_normaldata$X93077 * -1

topMRFscaled <- data.frame(scale(topMRF_normaldata))  # scales the data to z-scores of each indicator per area.
#view(top15scaled)

# Calculation of Mean Z-score per Area
topMRFzmean <- topMRFscaled

topMRFzmean$MeanZ <- rowMeans(topMRFzmean)
#view(top15zmean)

# Isolation of Mean Z-score for each area. This allows the ranking of each area's healthcare landscape.

topMRFareameanz <- topMRFzmean %>%
  select(MeanZ) %>%
  rownames_to_column('Area') %>%
  mutate(Score = MeanZ * -1 + 10) %>%
  select(Area, Score) %>%
  arrange(desc(Score)) #%>%
  #view()
#view(top15areameanz)


```

```{r}
#england_map <- st_read(dsn = #"https://opendata.arcgis.com/datasets/25dc36af098744c6848f8228a09d87b3_0.geojson")
# 
mrf_scores <- select(topMRFareameanz, Area, Score)

mrf_england <- england_map %>% 
   left_join(y = mrf_scores, by = c("lad18nm" = "Area")) %>%
  select(Score, geometry) %>%
  filter(is.na(Score) == FALSE)

 plot(mrf_england, main = "Modifiable Risk Factors in England")
```
```{r}
Mean <- mean(topMRFareameanz$Score)
sdv <- sd(topMRFareameanz$Score)
Median <- median(topMRFareameanz$Score)

Mean
sdv
Median
```
```{r}
# Correlation between indicators
# Credits to Nanjo Atsunori

topMRF_cor <- cor(topMRFscaled)
corrplot(topMRF_cor, type = "upper", order = "hclust", 
         tl.col = "black", tl.srt = 45)
```



